---
title: "An example of using the zipfs package on the text of Dracula"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{dracula}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  eval = FALSE # since package isn't written yet
)
```

```{r setup}
library(zipfs)
```

A character string of lines from the book Dracula.  Obtained from Gutenberg
```{r}
?dracula
dracula[1:20]
```


Provide `book_meta()` to extract useful book meta data from a Gutenberg book, need to provide the relevant lines from header:
```{r}
book_meta(dracula[1:20])
```

`count_words()` counts occurrences of every word in a character string
```{r}
word_frequency <- count_words(dracula)
word_frequency
```

A rank frequency plot can be created by passing in the counts to  `plot_rank()`:
```{r}
word_frequency %>% 
  pull(n)
  plot_rank()
```

A line based on the maximum likelihood estimate for $\alpha$ can be
added to the plot by adding the argument `add_fit = TRUE`:
```{r}
word_frequency %>% 
  pull(n)
  plot_rank(add_fit = TRUE)
```

Or, if only the estimate is desired, it can be computed with `fit_zipfs()`, again passing in only the counts:
```{r}
word_frequency %>% 
  pull(n) %>% 
  fit_zipfs()
```
