---
title: "Implementation Notes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{zipfs-law-dracula}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

A place to keep track of code, notes and brainstorming for the zipfs package.

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Also look into  gutenbergr https://github.com/ropensci/gutenbergr

# Example Code 

```{r setup, message = FALSE}
library(tidyverse)
library(here)
```

```{r}
dracula <- read_lines(here("inst", "extdata", "dracula.txt"))
```

## Book Summaries

Do something with this?
```{r}
dracula[10:17] 
```

```{r}
extract_element <- function(text, element){
  text  %>% 
  str_subset(element) %>% 
  str_remove(paste0(element, ": "))
}

dracula[10:17] %>% 
  get_meta("Author")

book_meta <- function(text){
  tibble(
    author = get_meta(text, "Author"),
    title = get_meta(text, "Title"),
    release = get_meta(text, "Release Date")
  )
}

dracula[10:17] %>% 
  book_meta()
```

Using this to summarise all books:
```{r}
books <- tibble(
  file = fs::dir_ls(here("inst", "extdata"), glob = "*.txt"),
)

books %>% 
  rowwise(file) %>% 
  mutate(text = list(read_lines(file))) %>% 
  summarise(book_meta(text[1:20]), .groups = "rowwise")
```

## Word Counts

From https://merely-useful.github.io/py-rse/scripting.html#scripting-wordcount
```
the,8036
and,5896
i,4712
to,4540
of,3738
a,2961
in,2558
he,2543
that,2455
it,2141
```

### tidytext approach

Word frequency:
```{r}
library(tidytext)
dracula_tbl <- tibble(text = dracula)

dracula_freq <- 
  dracula_tbl %>% 
  unnest_tokens("word", text) %>% 
  count(word, sort = TRUE)
dracula_freq
```

Doesn't match output in py-rse. Why?

### stringr approach

```{r}
dracula <- read_lines(here("inst", "extdata", "dracula.txt"))

chunks <- 
  dracula %>% 
  str_to_lower() %>% 
  # split by one or more whitespace characters
  str_split("\\s+") %>% 
  unlist()

words <- 
  chunks %>% 
  # remove punctuation
  str_remove_all(pattern = "[[:punct:]]+")
  
# get rid of empty strings
words <- words[words != ""]  

words %>% table() %>% 
  sort(decreasing = TRUE) %>% 
  head(n = 10)
```

Much closer to py-rse, only off by 1 on "the".

I'm removing all punctuation but in py-rse, we only remove leading and trailing punctuation. Is that the difference?

```{r}
words <- 
  # str_split() always returns a list
  chunks %>% 
  # remove punctuation
  str_remove(pattern =  "^[[:punct:]]+") %>% 
  str_remove(pattern =  "[[:punct:]]+$") 

# get rid of empty strings
words <- words[words != ""]  

words %>% table() %>% 
  sort(decreasing = TRUE) %>% 
  head(n = 10)  
```


### base approach

```{r}
dracula <- read_file(here("inst", "extdata", "dracula.txt"))
chunks <- unlist(strsplit(tolower(dracula), split = "\\s+"))

words2 <- gsub(pattern = "[[:punct:]]+", replacement = "", chunks) 
words <- words[words != ""]  

word_freq <- table(words) 
head(sort(word_freq, decreasing = TRUE), n = 10)

dracula_freq <- tibble(word = names(word_freq), n = as.numeric(word_freq)) %>% 
  arrange(desc(n))
```


## Plots

Compare to: https://merely-useful.github.io/py-rse/figures/git-cmdline/plot-initial.png

```{r}
dracula_freq %>% 
  ggplot(aes(n, 1/rank(desc(n), ties = "max"))) +
  geom_point() +
  labs(
    title = "Inverse rank frequency plot",
    x = "Word frequency",
    y = "Inverse Rank")
```

Compare to: https://merely-useful.github.io/py-rse/figures/git-cmdline/plot-loglog.png

```{r}
dracula_freq %>% 
  ggplot(aes(n, rank(desc(n), ties = "max"))) +
  geom_line() +
  geom_point() +
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Rank frequency plot",
    x = "Word frequency",
    y = "Rank")
```

## Fit

```{r}
dpower <- function(x, alpha){
  beta <- 1/alpha + 1
  (1/x)^(beta - 1) - (1/(x + 1))^(beta - 1)
}

# negative log likelihood l(beta) = -sum(log(f(x)))
nllpower <- function(alpha, x){
  - sum(log(dpower(x = x, alpha = alpha)))
}

# Optimizer settings from @moreno2016large
# fix lower and upper for using alpha as parameter not beta
mle <- optim(1.5, nllpower, x = dracula_freq$n, 
  lower = 1, upper = 4, 
  hessian = TRUE, method = "Brent")

(alpha_hat <- mle$par)
# Standard error from ML theory
se <- sqrt(1/mle$hessian)[1, 1]

# Asymptotic 95% CI
(ci <- alpha_hat + c(-1, 1) * 1.96 * se)
```


Compare to: https://merely-useful.github.io/py-rse/figures/git-advanced/dracula-fit.png
```{r}
n <- nrow(dracula_freq)
dracula_freq %>% 
  ggplot(aes(n, rank(desc(n), ties = "max"))) +
  geom_point(size = 0.5, color = "grey50") +
  geom_abline(
    intercept = log10(n),
    slope = - 1/alpha_hat
  ) + 
  scale_x_log10() +
  scale_y_log10() +
  labs(
    title = "Rank frequency plot with fitted power law",
    x = "Word frequency",
    y = "Rank"
    )
```

# Brainstorming Interface

```{r}
knitr::opts_chunk$set(eval = FALSE)
```


What will the actual vignette look like?

```{r}
file <- here("inst", "extdata", "dracula.txt") 
word_freq <- count_words(path = dracula_file)

plot_rank(word_freq, "n")
plot_rank(word_freq, n)
plot_rank(word_freq$n)

fit <- fit_zipfs(word_freq$n)
fit <- fit_zipfs(word_freq)
fit <- fit_zipfs(word_freq, n)
fit
# slope, alpha = ?, se = ?, intercept?



fit_zipfs(word_freq$n)

# This way of using it seems useful
books %>% 
  group_by(title) %>% 
  summarize(fit_zips(n))

# Or alternatively
books %>% 
  group_by(title) %>% 
  summarise(alpha = fit_zips(n))

dracula %>% 
  word_count() %>% 
  summarise(fit_zipfs(n))

# Suggests signature
fit_zips <- function(n){}

# What should output be?
# something that prints OK alone,
# fits in tibble, and
# easily used by plotting function to add a line
# just alpha?  SE as well?

# But for plotting, might be easier to 
# use ggplot syntax, i.e. tibble in, then specify column, 
# allows for facettng, coloring etc.
# but where should dots go ...?


# Could use S3 so can have an `autoplot()` function -> `plot()` method
# for word_count data (i.e. make output from `count_words()`, have a class).
# But S3 is probably beyond the audience here
plot(word_freq)

# Technically only need n to make plot (and fit data and add line)
# so maybe just having the interface as
plot_rank(word_freq$n, add_fit = TRUE)
# no way to control colors, lines, other aesthetics.

# Then can't do
books %>% 
  plot_rank() +
  facet_wrap(~ title)

# But could do
books %>% 
  rowwise() %>% 
  mutate(plot = plot_rank(n, add_fit = TRUE)) %>% 
  pull(plot) %>% 
  walk(print) # or save out to files
```


```{r}
files <- fs::dir_ls(here("inst", "extdata"), glob = ".txt")
```


